Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-18 Scripts/Initial_Analysis.Rmd
Re-organized results

```{r PropChange, eval = F, echo =F}

# Get taxon list
Taxon_List <- list.files(paste(my_path("R"),"Proportion_2005",sep=""))

# clean names for function
Taxon_List <- gsub(".*_","",Taxon_List) 
Taxon_List <- gsub("\\..*","",Taxon_List)

# Run results
results <- PropChange(Taxon_List, links="y") %>% 
  filter(!is.na(eez_neighbour)) %>% 
  mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
                           ifelse(per_mid <= -50,-50,per_mid)
                           ),
         per_early_plot =ifelse(per_early >= 50, 50,
                           ifelse(per_early <= -50,-50,per_early)
                           )
         )

# For dat availabillity
 # write_csv(results,
          # "proportion_change_2005.csv")

results <- my_path("R",name="proportion_change_2005.csv", read=T)

# View(results)

### Load Data

@@

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  clean_names()

# Call world map from natural earth
World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>% 
  rename(fishing_entity = name_long) %>% 
  clean_names()

eez_centroid <- my_path("D",extra_path = "Spatial",name = "eez_centroids.csv",read = T)

@@

####  Year of Eergence Analysis

```{r Emergence-analysis, eval = F, echo =F}

# Get taxon list
Taxon_List <- list.files(my_path("R",extra_path = "Emergence_2005"))

# clean names for function
Taxon_List <- gsub("_.*","",Taxon_List)

### Load Data

>>>>

#### Data Needed for Analysis

```{r General_Data, eval = F, echo =F}

# --------------- #
# General Data needed
# --------------- #

# Get taxon list
Taxon_List_emer <- list.files(my_path("R",extra_path = "Emergence_2005"))

# clean names for function
Taxon_List_emer <- gsub("_.*","",Taxon_List_emer)

# --------------- #
# Load Proportion results
# --------------- #

# Read proportion results
# prop_results <- PropChange(Taxon_List, links="y") %>% 
  # filter(!is.na(eez_neighbour)) %>% 
  # mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
  #                          ifelse(per_mid <= -50,-50,per_mid)
  #                          ),
  #        per_early_plot =ifelse(per_early >= 50, 50,
  #                          ifelse(per_early <= -50,-50,per_early)
  #                          )
  #        )

# For dat availabillity
 # write_csv(prop_results,
          # "proportion_change_2005.csv")

prop_results <- my_path("R",name="proportion_change_2005.csv", read=T)

# --------------- #
# Load year of emergence results
# --------------- #

# --------------- #
# Load shapefiles for figures
# --------------- #

@@

@@

####  Year of Eergence Analysisç
